---
title: "2018-11-07"
output: html_notebook
---
```{r}
民國年月<-c("099/01","099/02","099/03")
```

```{r}
library(stringr)
library(lubridate)
民國年月<-c("099/01","099/02","099/03")

# 1
str_c("1",民國年月,"/01")->民國年月

# 2
lubridate::ymd(民國年月) -> 民國年月

# 3
民國年月 + years(911)
```
```{r}
民國年月<-c("099/01","099/02","099/03")

library(dplyr)
# 1
民國年月 %>% 
  str_c("1", . ,"/01") %>%
  ymd %>%
  { . + years(911) }
```

```{r}
library(dplyr)
```

```{r}
library(readr)
collegeData <- read_csv("https://quality.data.gov.tw/dq_download_csv.php?nid=6231&md5_url=dda8fca407131483c1d8cbf3d61cf793")
```

```{r}
library(dplyr)
mutate(
  collegeData,
  學校代碼1=as.factor(學校代碼),
  學校名稱2=as.factor(學校名稱)
  ) -> collegeData2
```

```{r}
collegeData %>%
  mutate(.,
  學校代碼=as.factor(學校代碼),
  學校名稱=as.factor(學校名稱)
  ) ->collegeData2
```
```{r}
collegeData$學校代碼<-as.factor(collegeData$學校代碼)
collegeData$學校名稱<-as.factor(collegeData$學校名稱)
collegeData -> collegeData2
```

```{r}
library(stringr)
collegeData %>%
  mutate( #將所有逗號拿掉
    一年級男生=str_replace(一年級男生,",",""),
    一年級女生=str_replace(一年級女生,",","")
    ) %>%
  mutate( #將字串轉成數值
    一年級男生=as.numeric(一年級男生),
    一年級女生=as.numeric(一年級女生)
    ) -> collegeData3
collegeData3$一年級男生
    
```




```{r}
collegeData %>% 
  mutate( #將所有逗號拿掉
    `日間∕進修別`=as.factor(`日間∕進修別`),
    等級別=as.factor(等級別),
    一年級男生=as.numeric(一年級男生),
    一年級女生=as.numeric(一年級女生)
  ) -> collegeData3
```

```{r}
library(readr)
cl<-locale(grouping_mark = ",") # 創造cl來描述千分位符號使用","的習慣場景
collegeData %>% 
  mutate(
    `日間∕進修別`=as.factor(`日間∕進修別`),
    等級別=as.factor(等級別),
    一年級男生=parse_number(一年級男生,na=c("","NA","-"),locale=cl),
    一年級女生=parse_number(一年級女生,na=c("","NA","-"),locale=cl)
  ) -> collegeData4
```

```{r}
collegeData %>% 
  mutate(
    `日間∕進修別`=as.factor(`日間∕進修別`),
    等級別=as.factor(等級別),
    一年級男生=parse_number(一年級男生,locale=cl),
    一年級女生=parse_number(一年級女生,locale=cl),
    一年級男生每千人=一年級男生/1000,
    一年級女生每千人=一年級女生/1000
    ) -> collegeData5
```

```{r}
college1stYearData %>%
  mutate(
    一年級男生=parse_number(一年級男生,local=c1),
    一年級女生=parse_number(...),
    二年級男生=parse_number(...),
    二年級女生=parse_number(...),
  )
```














Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
