---
title: "2018-09-26"
output: html_notebook
---
```{r}
a<-5
a2<-5L
```

```{r}
aVector<-c(5,6,7)
a2Vector<-c(5L,6L,7L)
```

```{r}
b<-"你好"
bVector<-c("你好","How are you?")
```

<<<<<<< HEAD
```{r}
round(2.3875)
```

```{r}
round(2.3875,digits =2)
```

```{r}
library(readr)
student <- read_csv("https://raw.githubusercontent.com/tpemartin/course-107-1-programming-for-data-science/master/data/student.csv")
library(dplyr)
library(magrittr)
student %<>% mutate(
  身高級距=cut(身高,c(0,150,155,160,165,170,175,180,185,200)))
```


```{r}
as.factor(student$出生地) -> student$出生地
```

```{r}
levels(student$出生地)
```

=======
>>>>>>> 40aaed3709c7b875e9ceef51c9c7b8d24fd23d28

```{r}
table(student$'出生地')
```

```{r}
as.factor(student$入學年) -> student$入學年
as.factor(student$性別) -> student$性別
```

```{r}
levels(student$'入學年')
levels(student$性別)
```

```{r}
table(student$'入學年')
table(student$'性別')
```


```{r}
factor(student$身高級距,
       levels=c("(0,150]","(150,155]", "(155,160]", "(160,165]" ,"(165,170]", "(170,175]" ,"(175,180]" ,"(180,185]", "(185,200]"),
       ordered=TRUE) -> student$身高級距
```
```{r}
heightLevels <- c("(0,150]","(150,155]", "(155,160]", "(160,165]" ,"(165,170]", "(170,175]" ,"(175,180]" ,"(180,185]", "(185,200]")
factor(student$'身高級距',
       levels=heightLevels,
       ordered=TRUE) -> student$'身高級距'
```

```{r}
a<-"2017-01-31"
```


```{r}
library(dplyr)
library(lubridate)
a <- ymd("2017-01-31") 
b <- ymd_hms("2017-01-31 20:11:59")
```

```{r}
a <- ymd("2017/01/31") 
b <- ymd_hms("2017-01-31 2:53:00pm")
```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
